---
title: "Assignment 1"
author: "Austin Richards"
date: "5/3/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

```


```{r}
Parcels_raw <- 
  
  read_delim("parcels.csv.zip",
             delim = ",",
             col_types = cols(.default = col_character()))
```



```{r}
#parse specificiations taken from PDF, making sure nas are read collectly, only specifying parse for those taht aren't character (default set above)

Parcels <- transmute(Parcels_raw, na = 'NA', 
  Situs1 = Situs1, na = 'NA', 
  Situs2 = Situs2,na = 'NA', 
  Acreage = parse_double(Acreage),na = 'NA', 
  UseCode = UseCode,na = 'NA', 
  NonTaxCode = NonTaxCode,na = 'NA', 
  AgPres = AgPres,na = 'NA', 
  Land_Value = parse_double(LandValue),na = 'NA', 
  Net_Impr = parse_double(Net_Impr),na = 'NA', 
  Net_Av = parse_double(Net_AV),na = 'NA', 
  M_Address1 = M_Address1, na = 'NA', 
  M_Address2 = M_Address2, na = 'NA'
)

```

```{r}
#confiriming R is recognizing my NAs as NAs

any(is.na(Parcels))
```

```{r}
Parcels <- as.tibble(Parcels)

write_delim(Parcels, "parcels.csv", delim = "|") #writing csv with | as deliminator
```


```{r}
summary(Parcels)
```


1) What are the 10 most-frequently-occuring land uses (in descending order)?
Hint: Load the UseCodes into a separate tibble, then join it to the parcels tibble.


```{r}
Usecodes<- read_delim("UseCodes.csv", delim = "|")
```

```{r}
Parcels <- left_join(Usecodes, Parcels, by=("UseCode"))

```


```{r}
most_common <- table(Parcels$CodeDesc) %>% 
  as.data.frame() %>% 
  top_n(11,Freq) %>% #Using 11 because when using 10, one of the most common occurences is "no descripiton available"
  arrange(desc(Freq)) 

colnames(most_common) <- c("Landuse Type", "Occurences")

most_common
 


```

Most Common Landuse Types in Our Dataset:

1) Single Family Residence	73915	
2) Residential Rentals	4985	
3) Sited inside M/H Park (Rented)	4540	
4) Vacant Land	4382	
5) Condo	3791	
6) Double Wide New Const. (after 7/1/80)	1718	
7) Apartments (5 or more units)	1486	
8) Rec. Area - 5-6 class, 1000-1300 sq.ft.	1423	
9) Planned Unit Development	1124
10) Retail Stores, Single Story	1024	


No Description Available	1136	



2) How many acres are in agricultural preserves?
Assume agricultural preserves are indicated by non-NA values for AgPres.


```{r}
Preserves <- filter(Parcels, AgPres != 'NA')

sum(Preserves$Acreage)
```

 549563.4
 
 
3)What is the mean net assessed value per acre of the entire county?
i.e., as if the entire county were a single parcel.

```{r}
total_value<- filter(Parcels, Land_Value != 'NA') 
 value <- sum(total_value$Land_Value)

total_acreage <-filter(Parcels, Acreage != 'NA') 
acreage <- sum(total_acreage$Acreage)

value/acreage



```

$16749.96

```{r}

##I want to maake sure I didn't miss any values after removing NAs (i.e. if one row had an NA for Land Value but not for Acreage, or vice-versa, the answer above would not hold

check_1 <- subset(Parcels, is.na(Acreage)) 
check_2 <- subset(Parcels, is.na(Land_Value)) 

summary(check_1$Land_Value)
summary(check_2$Land_Value)

#confirmed-we're good, answer above is correct
```


4)What is the total net assessed value of all non-taxable parcels?
Assume non-taxable parcels are indicated by non-NA values for NonTaxCode.

```{r}
non_taxable <- filter(Parcels, NonTaxCode != 'NA')
sum(non_taxable$Net_Av)

#net assesed value represented by column Net_Av (I know this from .pdf file)
```
$1093026091

5) What are the 10 largest property holders, by acreage?
Use the complete mailing address for tax statements as a proxy for the parcel owner. Ignore parcels where either component of the address is NA.


aggregate_field <- aggregate(value_perha ~ id + ag4a_04, FUN = sum, data=joined_df)

```{r}
complete_address <- filter(Parcels, M_Address1 != 'NA' & M_Address2 != 'NA') %>% 
  unite(Address_Full, c("M_Address1", "M_Address2"), sep = " ", remove = TRUE) #filtering observations without a complete address to comply with second part of instructionsm and then making a new column which has full address  (M1 and M2 ombined)




ag_acre <- aggregate(Acreage ~ Address_Full, FUN = sum, data = complete_address)  #aggregating the acreage owned by each landowner


top_prop_acre <- ag_acre %>% 
top_n(10, Acreage) %>% 
arrange(desc(Acreage)) #taking top 10 acreage holders and placing them in decending order

top_prop_acre #answer
```

785 MARKET ST SAN FRANCISCO CA 94103-	37860.00
166 PARADISE RD SANTA BARBARA CA 93105-	30109.71
PO BOX 573 LAKE ARROWHEAD CA 92352-	24262.89
870 MARKET ST 1100 SAN FRANCISCO CA 94102-	23833.67
2491 BULL CANYON RD SANTA MARIA CA 93454-	18594.80
201 MISSION ST 4TH FLR SAN FRANCISCO CA 94105 1831-	16640.00
PO BOX 340 SAN LUCAS CA 93954-	15373.61
PO BOX 9 SAN JUAN CAPISTRANO CA 92693-	10170.02
2300 EAST VALLEY RD SANTA BARBARA CA 93108-	9800.95
PO BOX 338 SANTA YNEZ CA 93460-	9189.45



6)What are the 10 largest property holders, by net assessed value?


```{r}



ag_val <- aggregate(Net_Av ~ Address_Full, FUN = sum, data = complete_address)  #aggregating the anet assesed value owned by each address


top_prop_value <- ag_val %>% 
top_n(10, Net_Av) %>% 
arrange(desc(Net_Av)) #taking top 10 acreage holders and placing them in decending order

top_prop_value #answer
```


737 GARDEN ST SANTA BARBARA CA 93101:	242575885
735 ANACAPA ST SANTA BARBARA CA 93101:	190784490
21 E VICTORIA ST 200 SANTA BARBARA CA 93101:	179642731
PO BOX 20130 SANTA BARBARA CA 93120 0130:	177735038
280 CHESTNUT WESTMONT IL 60559:	157323864
PO BOX 660248 DALLAS TX 75266 0248:	151925292
1260 CHANNEL DR SANTA BARBARA CA 93105:	120001340
645 FIFTH AVE 8 NEW YORK NY 10022:	118000000
500 STEVENS AVE 100 SOLANA BEACH CA 92075:	107926369
2235 FARADAY AVE O CARLSBAD CA 92008:	104533906

