---
title: "Assignment 2"
author: "Austin Richards"
date: "5/16/2019"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(DBI)
library(RSQLite)

```


```{r}
Parcels_raw <- 
  
  read_delim("parcels.csv.zip",
             delim = ",",
             col_types = cols(.default = col_character()))
```



```{r}

Parcels <- transmute(Parcels_raw, 
  Situs1 =  parse_character(Situs1, na = 'NA'), 
  Situs2 = parse_character(Situs2,na = 'NA'), 
  Acreage = parse_double(Acreage,na = 'NA'), 
  UseCode = parse_character(UseCode, na = 'NA'), 
  NonTaxCode = parse_character(NonTaxCode,na = 'NA'), 
  AgPres = parse_character(AgPres, na = 'NA'), 
  Land_Value = parse_double(LandValue,na = 'NA'), 
  Net_Impr = parse_double(Net_Impr,na = 'NA'), 
  Net_Av = parse_double(Net_AV,na = 'NA'), 
  M_Address1 = parse_character(M_Address1, na = 'NA'), 
  M_Address2 = parse_character(M_Address2, na = 'NA')
)

```

```{r}
#confiriming R is recognizing my NAs as NAs

any(is.na(Parcels))
```


```{r}
Parcels <- as.tibble(Parcels)
```

```{r}
UseCode <- read_delim("UseCodes.csv", delim = "|")
```


```{r}

db <- dbConnect(RSQLite::SQLite(), "parcels.db")
```


```{r}
#Overwrite = true so everything is replicable

dbWriteTable(db, "Parcel", Parcels, overwrite = TRUE)
dbWriteTable(db, "Codes", UseCode, overwrite = TRUE)
```

1) What are the 10 most-frequently-occuring land uses (in descending order)?

SELECT name,COUNT(*) as count FROM tablename GROUP BY name ORDER BY count DESC;

```{sql connection= db}

SELECT CodeDesc, COUNT(CodeDesc) AS parcels_quant
FROM Parcel JOIN Codes ON Parcel.UseCode = Codes.UseCode 
GROUP BY Parcel.UseCode
ORDER BY parcels_quant DESC
LIMIT 10


```




Most Common Landuse Types in Our Dataset:

1) Single Family Residence	73915	
2) Residential Rentals	4985	
3) Sited inside M/H Park (Rented)	4540	
4) Vacant Land	4382	
5) Condo	3791	
6) Double Wide New Const. (after 7/1/80)	1718	
7) Apartments (5 or more units)	1486	
8) Rec. Area - 5-6 class, 1000-1300 sq.ft.	1423	
9) Planned Unit Development	1124
10) Retail Stores, Single Story	1024	




2) How many acres are in agricultural preserves?
Assume agricultural preserves are indicated by non-NA values for AgPres.


```{sql connection= db}

SELECT SUM (Acreage)
FROM Parcel
WHERE AgPres IS NOT NULL 

```

 549563.4
 
 
3)What is the mean net assessed value per acre of the entire county?
i.e., as if the entire county were a single parcel.


```{sql connection= db}

SELECT SUM (NET_AV)/SUM(Acreage)
FROM Parcel
WHERE Acreage IS NOT NULL
AND NET_AV IS NOT NULL

```

$3402.63


4)What is the total net assessed value of all non-taxable parcels?
Assume non-taxable parcels are indicated by non-NA values for NonTaxCode.


```{sql connection= db}

SELECT SUM (NET_AV)
FROM Parcels
WHERE NonTaxCode
IS NOT NULL


```

$1093026091

5) What are the 10 largest property holders, by acreage?
Use the complete mailing address for tax statements as a proxy for the parcel owner. Ignore parcels where either component of the address is NA.


```{sql connection=db}


SELECT M_Address1, M_Address2, SUM(Acreage) AS Total_Acreage
FROM Parcels
WHERE M_Address1 IS NOT NULL
AND M_Address2 IS NOT NULL
GROUP BY M_Address1, M_Address2
ORDER BY Total_Acreage DESC
LIMIT 10

```




785 MARKET ST SAN FRANCISCO CA 94103-	37860.00
166 PARADISE RD SANTA BARBARA CA 93105-	30109.71
PO BOX 573 LAKE ARROWHEAD CA 92352-	24262.89
870 MARKET ST 1100 SAN FRANCISCO CA 94102-	23833.67
2491 BULL CANYON RD SANTA MARIA CA 93454-	18594.80
201 MISSION ST 4TH FLR SAN FRANCISCO CA 94105 1831-	16640.00
PO BOX 340 SAN LUCAS CA 93954-	15373.61
PO BOX 9 SAN JUAN CAPISTRANO CA 92693-	10170.02
2300 EAST VALLEY RD SANTA BARBARA CA 93108-	9800.95
PO BOX 338 SANTA YNEZ CA 93460-	9189.45



6)What are the 10 largest property holders, by net assessed value?

```{sql connection=db}

SELECT M_Address1, M_Address2, SUM(Net_AV) AS Total_Value
FROM Parcels
WHERE M_Address1 IS NOT NULL
AND M_Address2 IS NOT NULL 
AND Net_AV IS NOT NULL
GROUP BY M_Address1, M_Address2
ORDER BY Total_Value DESC
LIMIT 10

```


737 GARDEN ST SANTA BARBARA CA 93101:	242575885
735 ANACAPA ST SANTA BARBARA CA 93101:	190784490
21 E VICTORIA ST 200 SANTA BARBARA CA 93101:	179642731
PO BOX 20130 SANTA BARBARA CA 93120 0130:	177735038
280 CHESTNUT WESTMONT IL 60559:	157323864
PO BOX 660248 DALLAS TX 75266 0248:	151925292
1260 CHANNEL DR SANTA BARBARA CA 93105:	120001340
645 FIFTH AVE 8 NEW YORK NY 10022:	118000000
500 STEVENS AVE 100 SOLANA BEACH CA 92075:	107926369
2235 FARADAY AVE O CARLSBAD CA 92008:	104533906

